Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2018 (Coleoptera: Curculionidae), with notes on their distribution and phylogeny

### 2018-05-08 tex/manuscript.tex
some edits and recompile

\section*{Checklist of Species}\label{sec:checklist}
	RCC--5 articulations are provided in \textbf{bold font.} See \citet{jansen2015} for alignments of \textit{Minyomerus} concepts published from 1831 to 2015.

@@

\section*{Species Identification Key}\label{sec:idkey}
	\begin{xtabular}{@{}
                p{\dimexpr.1\textwidth-\tabcolsep\relax}
                p{\dimexpr.9\textwidth-\tabcolsep\relax}@{}}

@@

\section*{To Do}
	\begin{enumerate}[itemsep=-0.4em]
		\item Insert measurements.
		\item Submit names to zoobank.
		\item Upload matrix data to dryad.
		\item Upload pre-prints to bioR{\textchi}iv.
		\item Make sure all Checklist nomenclatural references are included -- Green 1920, Casey 1888, Pierce 1909, etc.
	\end{enumerate}

>>>>

\section*{Checklist of Species}\label{sec:checklist}
	RCC--5 articulations are provided in \textbf{bold font.} See \citet{jansen2015} for alignments of \textit{Minyomerus} concepts published from 1831 to 2015.

@@

\newpage
\section*{Species Identification Key}\label{sec:idkey}
	\begin{xtabular}{@{}
                p{\dimexpr.1\textwidth-\tabcolsep\relax}
                p{\dimexpr.9\textwidth-\tabcolsep\relax}@{}}

@@

\section*{To Do}
	\begin{enumerate}[itemsep=-0.4em]
		\item Submit names to zoobank.
		\item Upload matrix data to dryad.
		\item Upload pre-prints to bioR{\textchi}iv.
		\item Make sure all Checklist nomenclatural references are included -- Green 1920, Casey 1888, Pierce 1909, etc.
	\end{enumerate}
